---
title: 'DSC analysis: SuSiE versus smashr'
author: "Kaiqian Zhang"
date: "4/5/2019"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal 

The goal is to compare performance of `SuSiE` and `smashr` with respect to different kinds of underlying functions. 

## Method

While using `smashr`, we reflect the data when the number of data is not a power of 2. We simulate 30 datasets with different numbers of data points and various pves. We have the following seven methods.

- **smash_haar**: uses Haar wavelets in `smashr`. 

- **smash_s10**: uses Symlet 10 wavelets (filter.num=10) in `smashr`.

- **smash_s8**: uses Symlet 8 wavelets (filter.num=8) in `smashr`.

- **susie_haar**: uses Haar wavelets in `SuSiE`. Performs `SuSiE` with a fixed residual variance 0.01 as an initialization.

- **susie_haar_MAD**: uses Haar wavelets in `SuSiE`. Performs `SuSiE` with an estimated residual variance using MAD method (Donoho & Johnstone, 1994) as an initialization.

- **susie_s10**: uses Symlet 10 wavelets (filter.num=10) in `SuSiE`. Performs `SuSiE` with a fixed residual variance 0.01 as an initialization.

- **susie_s10_MAD**: uses Symlet 10 wavelets (filter.num=10) in `SuSiE`. Performs `SuSiE` with an estimated residual variance using MAD method as an initialization.

## Results summary

- Overall, `smashr` methods are better than `SuSiE` methods. Their mean squre errors have smaller mean and variance. 

- When pve is as small as 0.5, `smashr` has an apparent advantage over `SuSiE` in prediction. Please see `Figure for 100 data points and pve is 0.5` and `Figure for 300 data points and pve is 0.5`. 

- Most of the time, **susie_s10_MAD** has the best performance among all `SuSiE` methods. 

## Analysis details
```{r, include=FALSE}
library(ggplot2)
library(gridExtra)
library(ggpubr)
```


```{r}
dscout = readRDS("../data/susie-np-dscout30.RDS")
dscout.df = data.frame(dscout$simulate.n, dscout$simulate.pve, dscout$simulate.scenario, dscout$analyze, dscout$score.error)
names(dscout.df) = c("n", "pve", "scenario", "method", "mse")
```

### Suppose we have 100 data points.

#### Figures for 100 data points and pve is 0.99.  
```{r}
dscout.df1 = dscout.df[dscout.df$n==100 & dscout.df$pve==0.99,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```

#### Figures for 100 data points and pve is 0.95. 

```{r}
dscout.df1 = dscout.df[dscout.df$n==100 & dscout.df$pve==0.95,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```

#### Figures for 100 data points and pve is 0.9.
```{r}
dscout.df1 = dscout.df[dscout.df$n==100 & dscout.df$pve==0.9,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```

#### Figures for 100 data points and pve is 0.5.
```{r}
dscout.df1 = dscout.df[dscout.df$n==100 & dscout.df$pve==0.5,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```

### Suppose we have 300 data points.

#### Figures for 300 data points and pve is 0.99.
```{r}
dscout.df1 = dscout.df[dscout.df$n==300 & dscout.df$pve==0.99,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```

#### Figures for 300 data points and pve is 0.95.
```{r}
dscout.df1 = dscout.df[dscout.df$n==300 & dscout.df$pve==0.95,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```

#### Figures for 300 data points and pve is 0.9.
```{r}
dscout.df1 = dscout.df[dscout.df$n==300 & dscout.df$pve==0.9,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```

#### Figures for 300 data points and pve is 0.5.
```{r}
dscout.df1 = dscout.df[dscout.df$n==300 & dscout.df$pve==0.5,]

dscout.df1.angles = dscout.df1[dscout.df1$scenario=="angles",]
angles = ggplot(aes(y=mse, x=method), data=dscout.df1.angles) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: angles") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blip = dscout.df1[dscout.df1$scenario=="blip",]
blip = ggplot(aes(y=mse, x=method), data=dscout.df1.blip) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blip") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.blocks = dscout.df1[dscout.df1$scenario=="blocks",]
blocks = ggplot(aes(y=mse, x=method), data=dscout.df1.blocks) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: blocks") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.bumps = dscout.df1[dscout.df1$scenario=="bumps",]
bumps = ggplot(aes(y=mse, x=method), data=dscout.df1.bumps) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: bumps") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.doppler = dscout.df1[dscout.df1$scenario=="doppler",]
doppler = ggplot(aes(y=mse, x=method), data=dscout.df1.doppler) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: doppler") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

dscout.df1.spikes = dscout.df1[dscout.df1$scenario=="spikes",]
spikes = ggplot(aes(y=mse, x=method), data=dscout.df1.spikes) +
  geom_violin(alpha=0.5, color="black") + 
  geom_jitter(alpha=0.5, aes(color=method), position = position_jitter(width = 0.1)) + 
  coord_flip() + 
  ggtitle("scenario: spikes") + 
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=10), axis.text.x = element_text(angle = 90, hjust = 1))

ggarrange(angles, blip, blocks, bumps, doppler, spikes, ncol=3, nrow=2, common.legend = TRUE, legend="bottom")
```
